### 2020-04-04 06b-bisimulation.tex
cambi piccoli
cambi piccoli

For example we would like to express properties about each step of the simulation of a system like the following:
\begin{enumerate}
\item Has the entity $s_i$ been used by rule $r_j$ as reagent?
\item Has the entity $s_i$ blocked the application of  rule $r_j$?
\item Has the entity $s_i$ been produced by rule $r_j$?
\item Has the entity $s_i$ been produced by some rule?
\item Has the entity $s_i$ been provided by the context? 
\item Has the rule $r_j$ not been applied? 
%\item Has the entity $s$ been used by some rule as reagent ?
%\item Has the entity $s$ blocked  the application of some rules ?
%\item Has the entity $s$ been produced ?
%\item Has the entity $s$ been provided by the context ?
%\item Has the rule $i$ been applied ?
\end{enumerate}

@@

The corresponding formulas to the sample queries listed above are as follows:\\

>>>>

For instance we would like to express properties about each step of the simulation of a system like in the following:

\begin{example} \label{properties_ex}
\begin{enumerate}
\item Has the entity $s_i$ been used by rule $r_j$ as reagent?
\item Has the entity $s_i$ blocked the application of  rule $r_j$?
\item Has the entity $s_i$ been produced by rule $r_j$?
\item Has the entity $s_i$ been produced by some rule?
\item Has the entity $s_i$ been provided by the context? 
\item Has the rule $r_j$ not been applied? 
%\item Has the entity $s$ been used by some rule as reagent ?
%\item Has the entity $s$ blocked  the application of some rules ?
%\item Has the entity $s$ been produced ?
%\item Has the entity $s$ been provided by the context ?
%\item Has the rule $i$ been applied ?
\end{enumerate}
\end{example}

@@

The formulas corresponding to the sample queries listed in Example~\ref{properties_ex} are as follows:

### 2020-04-04 07-discussion.tex
cambi piccoli
cambi piccoli

As we have briefly sketched, our model of two \emph{communicating Reaction Systems} 
can enable the study of the behaviour of one RS
in relation to another one.
In Example~\ref{ex:twoRS} describing  the behaviour of the \emph{lac} operon,
the two entities lactose and glucose are controlled 
non deterministically by the context.
In our framework,
instead, by exploiting the expressivity of c\CNA, 
the \emph{lac} operon system has been connected with the two systems 
producing the lactose and the glucose.
This way, the presence of these two entities in the \emph{lac} operon system 
can be regulated by realistic mechanisms.
%which can be modified to represent pathological states as well.

>>>>

As we have briefly sketched, our model of two 
 \emph{communicating Reaction Systems} can enable the study of the behaviour of one RS in relation to another one. 
Thus, the products of the reactions of one RS can become the input for another one. 
This could allow for a modular approach to modeling complex systems, by composing different Reaction Systems.

%which can be modified to represent pathological states as well.
